Distributed Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2017-01-23 R0V0.tex
Finish to write about the ADMM on the chain topology case

\mypara Solving the matrix inequality~\eqref{eq:Artstein-Sontag:inequality:dual} with ADMM, the components of the matrix $W$ obtained are shown in Equation~??

\begin{figure*}
\begin{align*}
	W_1(q_1)=1\times10^{-7}\begin{bmatrix}
	18-15x_1-28y_1+11.2y_1^2+3.2x_1^2+1.2x_1y_2&9.3+35x_1-43y_1+28y_1^2-16x_1^2-16x_1y_1\\
	*&4.9+40x_1-37y_1+72y_1^2+84x_1^2-155x_1y_1
	\end{bmatrix}\;,\\
	W_2(q_2)=1\times10^{-7}\begin{bmatrix}1-3.7x_2+2.3y_2+1.3y_2^2+3.5x_2^2-4.3x_2y_2&
	-0.6-0.6x_2+y_2+2y_2^2+3.5x_2^2-5.5x_2y_2\\
	*&0.4+2.3x_2-2.3y_2+3.3y_2^2+3.4x_2^2-6.7x_2y_2
	\end{bmatrix}\;,\\
	W_3(q_3)=1\times10^{-7}\begin{bmatrix}
		127-248x_3+18y_3+y_3^2+122x_3^2-18x_3y_3&
		-98+146x_3+19y_3+1.9y_3^2-50x_3^2-22x_3y_3\\
		*&76-78x_3-42y_3+6.4y3^2+21x_3^2+20x_3y_3
	\end{bmatrix}\;,\\
	W_4(q_4)=1\times10^{-6}\begin{bmatrix}
	22+4x_4-17y_4+8.8y_4^2+9.4x_4^2+12x_4y_4&
	-8.6-5.9x_4+1.8y_4-4.2y_4^2-9.7x_4^2-12x_4y_4\\
	*&4.3+7.5x_4+2.8y_4+3.2y_4^2+10x_4^2+11x_4y_4
	\end{bmatrix}\;.
\end{align*}
\end{figure*}

\begin{table}
	\begin{tabular}{r|l}
	Method&Time taken by the solver [s]\\ \hline
	Chordal graph decomposition&2.6 to 98\\
	ADMM&
	\end{tabular}
\end{table}

@@

\mypara Using ADMM to compute a solution to the MI~\eqref{eq:Artstein-Sontag:inequality:dual}, the solver took 96[s] and the obtained matrix $W$ has the components shown in

\begin{figure*}
	\begin{subequations}
	\begin{equation}\label{eq:}
		\resizebox{.9\textwidth}{!}{$W_1(q_1)=1\times10^{-5}\begin{bmatrix}
		4+3x_1-1\times10^3y_1+1\times10^{5}y_1^2+5x_1^2-1\times10^{3}x_1y_1&2+6x_1-5\times10^2y_1-6\times10^{2}y_1^2+3x_1^2-8\times10^{2}x_1y_1\\
		*&2+4x_1+3y_1+3y_1^2+5x_1^2+8x_1y_1
		\end{bmatrix}\;,$}
	\end{equation}
	\begin{equation}\label{eq:}
		\resizebox{.9\textwidth}{!}{$W_2(q_2)=1\times10^{-5}\begin{bmatrix}
		5+9x_2-2\times10^3y_2+1\times10^{5}y_2^2+4x_2^2-1\times10^{3}x_2y_2&6+11x_2-1\times10^{3}y_2-7\times10^{2}y_2^2+5x_2^2-9\times10^{2}x_2y_2\\
		*&7+12x_2+10y_2+4y_1^2+6x_1^2+9x_2y_2
		\end{bmatrix}\;,$}
	\end{equation}
	\begin{equation}\label{eq:}
		\resizebox{.9\textwidth}{!}{$W_3(q_3)=1\times10^{-5}\begin{bmatrix}
		7+16x_3-2\times10^3y_3+1\times10^{5}y_3^2+12x_3^2-2\times10^{3}x_3y_3&10+20x_3-1\times10^{3}y_3+1\times10^{3}y_3^2+11x_1^2-11\times10^{3}x_3y_3\\
		*&20+29x_3+29y_3+13y_3^2+13x_3^2+24x_3y_3
		\end{bmatrix}\;,$}
	\end{equation}
	\begin{equation}\label{eq:}
		\resizebox{.9\textwidth}{!}{$W_4(q_4)=1\times10^{-5}\begin{bmatrix}
		11+17x_4-2\times10^3y_4+1\times10^{5}y_4^2+9x_4^2-2\times10^{3}x_4y_4&13+21x_4-1\times10^{3}y_4+1\times10^{3}y_4^2+10x_4^2-1\times10^{3}x_4y_4\\
		*&20+27x_4+24y_4+11y_4^2+12x_4^2+18x_4y_4
		\end{bmatrix}\;,$}
	\end{equation}
	\end{subequations}
\end{figure*}

>>>>

\mypara Solving the matrix inequality~\eqref{eq:Artstein-Sontag:inequality:dual} with ADMM, the components of the matrix $W$ obtained are shown in the set of Equations~\eqref{eq:ADMM:chain case}. A summary of the time taken by the solver employing chordal graph and ADMM approach is shown in Table~\ref{tab:chain case}.

\begin{figure*}
\begin{subequations}\label{eq:ADMM:chain case}
	\begin{equation}
		\resizebox{.9\textwidth}{!}{$W_1(q_1)=1\times10^{-6}\begin{bmatrix}
		2-7x_1-10^3y_1+10^7y_1^2+10x_1^2-8.9\times10^2x_1y_1&
		0.5+0.6x_1-5.6\times10^2y_1-3\times10^2y_1^2-9x_1^2-4.1\times10^2\\
		*&0.4+4x_1-3y_1+6y_1^2+10x_1^2-16x_1y_1
		\end{bmatrix}$}
	\end{equation}
	\begin{equation}
		\resizebox{.9\textwidth}{!}{$W_2(q_2)=1\times10^{-6}\begin{bmatrix}
		4-2x_2-4\times10^3y_2+10^7y_2^2+x_2^2-5\times10^3x_2y_2&
		2-5x_2-2.5\times10^3y_2-2.3\times10^3y_2^2+3.2x_2^2-2.5\times10^3x_2y_2\\
		*&1-3x_2+3y_2+3y_2^2+9x_2^2-8x_2y_2
		\end{bmatrix}$}
	\end{equation}
	\begin{equation}
		\resizebox{.9\textwidth}{!}{$W_3(q_3)=1\times10^{-6}\begin{bmatrix}
		58-43x_3-6.1\times10^2y_3+10^8y_3^2+9x_3^2-4\times10^2x_3y_3&
		-60-9x_3-2.4\times10^2y_3-4\times10^2y_3^2+11x_3^2-3.6\times10^2x_3y_3\\
		*&60+60x_3-64y_3+18y_3^2+16x_3^2-34x_3y_3
		\end{bmatrix}$}
	\end{equation}
	\begin{equation}
		\resizebox{.9\textwidth}{!}{$W_4(q_4)=1\times10^{-6}\begin{bmatrix}
		18.5+44x_4-3.2\times10^3y_4+9.3\times10^6y_4^2+29x_4^2-3.7\times10^3x_4y_4&
		-33-50x_4-2\times10^3y_4-2\times10^3y_4^2-9x_4^2-2.3\times10^3x_4y_4\\
		*&64+31x_4-26y_4+4.4y_4^2+5x_4^2-7x_4y_4
		\end{bmatrix}$}
	\end{equation}
\end{subequations}
\end{figure*}

\begin{table}
	\begin{tabular}{r|l}
	Method&Time taken by the solver (4 agents)\\ \hline
	Chordal graph decomposition&2.6s (decentralized)\\
	&3.5s (neighbor)\\
	&98s (unconstrained)\\
	ADMM&300s\\\hline
	\end{tabular}
	\caption{A summary of the time taken to solve the matrix inequalities \eqref{eq:MI formulation} and \eqref{eq:Artstein-Sontag:inequality:dual} using chordal graph decomposition and ADMM approaches, respectively, in the case of the chain topology}
	\label{tab:chain case}
\end{table}

@@

\mypara Using ADMM to compute a solution to the MI~\eqref{eq:Artstein-Sontag:inequality:dual}, the solver took 96[s] and the obtained matrix $W$ has the components shown in the set of Equations~\eqref{eq:ADMM:cyclic case}.

\begin{figure*}
	\begin{subequations}\label{eq:ADMM:cyclic case}
	\begin{equation}
		\resizebox{.9\textwidth}{!}{$W_1(q_1)=1\times10^{-5}\begin{bmatrix}
		4+3x_1-1\times10^3y_1+1\times10^{5}y_1^2+5x_1^2-1\times10^{3}x_1y_1&2+6x_1-5\times10^2y_1-6\times10^{2}y_1^2+3x_1^2-8\times10^{2}x_1y_1\\
		*&2+4x_1+3y_1+3y_1^2+5x_1^2+8x_1y_1
		\end{bmatrix}\;,$}
	\end{equation}
	\begin{equation}
		\resizebox{.9\textwidth}{!}{$W_2(q_2)=1\times10^{-5}\begin{bmatrix}
		5+9x_2-2\times10^3y_2+1\times10^{5}y_2^2+4x_2^2-1\times10^{3}x_2y_2&6+11x_2-1\times10^{3}y_2-7\times10^{2}y_2^2+5x_2^2-9\times10^{2}x_2y_2\\
		*&7+12x_2+10y_2+4y_1^2+6x_1^2+9x_2y_2
		\end{bmatrix}\;,$}
	\end{equation}
	\begin{equation}
		\resizebox{.9\textwidth}{!}{$W_3(q_3)=1\times10^{-5}\begin{bmatrix}
		7+16x_3-2\times10^3y_3+1\times10^{5}y_3^2+12x_3^2-2\times10^{3}x_3y_3&10+20x_3-1\times10^{3}y_3+1\times10^{3}y_3^2+11x_1^2-11\times10^{3}x_3y_3\\
		*&20+29x_3+29y_3+13y_3^2+13x_3^2+24x_3y_3
		\end{bmatrix}\;,$}
	\end{equation}
	\begin{equation}
		\resizebox{.9\textwidth}{!}{$W_4(q_4)=1\times10^{-5}\begin{bmatrix}
		11+17x_4-2\times10^3y_4+1\times10^{5}y_4^2+9x_4^2-2\times10^{3}x_4y_4&13+21x_4-1\times10^{3}y_4+1\times10^{3}y_4^2+10x_4^2-1\times10^{3}x_4y_4\\
		*&20+27x_4+24y_4+11y_4^2+12x_4^2+18x_4y_4
		\end{bmatrix}\;,$}
	\end{equation}
	\end{subequations}
\end{figure*}
